\documentclass{article}

\usepackage[margin=0.7in]{geometry}
\usepackage[parfill]{parskip}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{cite}

\begin{document}
	
\title{The Handshake Network}
	
\section{Motivation and Goals}

Wealth inequality in a capitalist society is an effective form of economic slavery. When
inflation becomes rampant, automation devalues labor, and wealthy individuals
accumulate disproportionate wealth via the Matthew Effect, freedom and well-being for the populace is
destroyed. Individual citizens cannot find quality housing, nutrition, healthcare, autonomy of
work, family stability, or recreation.

The United States economy at the beginning of the 21st century is increasingly digital, using
fiat US dollars as currency. Payments are no longer in the form of material goods or
promissory notes (which, historically, have been exchangeable for fixed amounts of valuable goods
in fixed supply, e.g., gold), but distributed as bits via digital banking networks. Indeed, the dollar
value of an asset has little resemblance to its intrinsic value. Wealthy groups and individuals -- for example,
the Federal Reserve, banks, and investment firms like BlackRock Financial -- are vested with authority to 
create digital currency and disperse it to other institutions of their choosing, often without
need for authorization from the public. Financial instruments such as options and derivatives are hedging mechanisms
that protect the wealth of these institutions by offloading failed risks to the public.



Here's a test citation \cite{sullivan2023}.

\section{Design}

\subsection{User Transactions Database}
\subsection{Global Inventory Database}

\subsection{Contracts}
\subsubsection{Contract Proposals}
\subsubsection{Contract Negotiations}
\subsubsection{Contract Finalization}
\subsubsection{Contract Fulfillment and Receipts}
\subsubsection{Contract Disputes}

\section{Contract Authorizations}

\section{Load Balancing}

\bibliographystyle{plain}
\bibliography{handshake}

\end{document}